# Genie set
```{r}
# score_data = score_data[,-5]
score_data["Driver_BH"] = driver_mutation_BH.1
score_data["Driver_BY"] = driver_mutation_BY.1
score_data
```

# TCGA set
```{r}
test_score_data["Driver_BH"] = test_driver_mutation_BH.1
test_score_data["Driver_BY"] = test_driver_mutation_BY.1

test_score_data
```

# Genie set alpha = 0.01
```{r}
# BH
# driver_mutation_BH.1
paste("Genie set BH:",sum(driver_mutation_BH.1))

# BY
# driver_mutation_BY.1C
paste("Genie set BY:",sum(driver_mutation_BY.1))
```

# TCGA set alpha = 0.01
```{r}
# BH
# test_driver_mutation_BH.1
paste("TCGA set BH:",sum(test_driver_mutation_BH.1))

# BY
# driver_mutation_BY.1C
paste("TCGA set BY:",sum(test_driver_mutation_BY.1))
```

# BH vs BY
```{r}
dataset = c("Genie","Genie","TCGA","TCGA")
method= c("BH","BY","BH","BY")
sigNo = c(sum(driver_mutation_BH.1),sum(driver_mutation_BY.1),sum(test_driver_mutation_BH.1),sum(test_driver_mutation_BY.1))
df = data.frame("Dataset" = dataset,"Method" = method,"SigNo" = sigNo)
df
```

# Check the mutation frequency for 176109 - 7166 = 168943
```{r}
diff_index = which(score_data$Gene_Codon %in% setdiff(score_data$Gene_Codon,test_score_data$Gene_Codon))
print(length(diff_index))
diff_part = score_data[diff_index,] %>%
  select(Gene_Codon,Sample_Freq,Driver_BH,Driver_BY)
diff_part %>% 
  arrange(.,desc(Sample_Freq))
```

```{r}
library(ggplot2)

ggplot(data=df, aes(x=Dataset, y=SigNo, fill=Method)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_text(aes(label=SigNo), vjust=-0.3, position = position_dodge(0.9), size=3.5)+
  scale_fill_brewer(palette="Paired") +
  ggtitle("No. of Potential Driver Mutations")+
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.title = element_blank()) 
  
```

# BH - overlap 1
```{r}
# Get the Gene_Codon of significant codons in Genie set
sig_genie_BH = score_data[which(score_data$Driver_BH == 1), c(1,3)]
paste("Genie significant:",nrow(sig_genie_BH))
sig_genie_BH

# Get the Gene_Codon of significant codons in TCGA set
sig_tcga_BH = test_score_data[which(test_score_data$Driver_BH == 1),c(1,3)]
paste("TCGA significant:",nrow(sig_tcga_BH))
sig_tcga_BH

# Get the intersected part (1,1)
intersect_1_BH = intersect(sig_genie_BH$Gene_Codon,sig_tcga_BH$Gene_Codon)
paste("Both significant:",length(intersect_1_BH))

# Get the unintersected part (1,0 / 0,1)
paste("only Genie Significant:",length(setdiff(sig_genie_BH$Gene_Codon,sig_tcga_BH$Gene_Codon)))
paste("Only TCGA Significant:",length(setdiff(sig_tcga_BH$Gene_Codon,sig_genie_BH$Gene_Codon)))
```

# BH - overlap 0
```{r}
# Get the Gene_Codon of non-significant codons in Genie set
nonsig_genie_BH = score_data[which(score_data$Driver_BH == 0),c(1,3)]
print(nrow(nonsig_genie_BH))
nonsig_genie_BH

# Get the Gene_Codon of non-significant codons in TCGA set
nonsig_tcga_BH = test_score_data[which(test_score_data$Driver_BH == 0),c(1,3)]
print(nrow(nonsig_tcga_BH))
nonsig_tcga_BH

# Get the intersected part (0,0)
intersect_0_BH = intersect(nonsig_genie_BH$Gene_Codon,nonsig_tcga_BH$Gene_Codon)
paste("Both insignificant:",length(intersect_0_BH))

# Get the unintersected part (0,1 / 1,0)
paste("only Genie non-Significant:",length(setdiff(nonsig_genie_BH$Gene_Codon,nonsig_tcga_BH$Gene_Codon)))
paste("Only TCGA non-Significant:",length(setdiff(nonsig_tcga_BH$Gene_Codon,nonsig_genie_BH$Gene_Codon)))
```

# 268 drivers BH
```{r}
drivers_BH = sig_genie_BH[which(sig_genie_BH$Gene_Codon %in% intersect_1_BH),]
drivers_BH = arrange(drivers_BH,desc(drivers_BH$Sample_Freq))
drivers_BH
```
```{r}
write.csv(drivers_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_drivers.csv", row.names = FALSE)
```


# 5887 non-driver-BY
```{r}
non_drivers_BH = nonsig_genie_BH[which(nonsig_genie_BH$Gene_Codon %in% intersect_0_BH),]
non_drivers_BH = arrange(non_drivers_BH,desc(non_drivers_BH$Sample_Freq))
non_drivers_BH
```
```{r}
write.csv(non_drivers_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_non_drivers.csv", row.names = FALSE)
```

# significance and non-significance in Genie BH
```{r}
write.csv(sig_genie_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_drivers_genie.csv", row.names = FALSE)
write.csv(nonsig_genie_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_non_drivers_genie.csv", row.names = FALSE)
```


# significance and non-significance in TCGA BYH
```{r}
write.csv(sig_tcga_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_drivers_tcga.csv", row.names = FALSE)
write.csv(nonsig_tcga_BH,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BH_non_drivers_tcga.csv", row.names = FALSE)
```







# BY - overlap 1
```{r}
# Get the Gene_Codon of significant codons in Genie set
sig_genie_BY = score_data[which(score_data$Driver_BY == 1),c(1,3)]
paste("Genie significant:",nrow(sig_genie_BY))
sig_genie_BY

# Get the Gene_Codon of significant codons in TCGA set
sig_tcga_BY = test_score_data[which(test_score_data$Driver_BY == 1),c(1,3)]
paste("TCGA significant:",nrow(sig_tcga_BY))
sig_tcga_BY

# Get the intersected part (1,1)
intersect_1 = intersect(sig_genie_BY$Gene_Codon,sig_tcga_BY$Gene_Codon)
intersect_1
paste("Both significant:",length(intersect_1))

# Get the unintersected part (1,0 / 0,1)
paste("only Genie Significant:",nrow(setdiff(sig_genie_BY$Gene_Codon,sig_tcga_BY$Gene_Codon)))
paste("Only TCGA Significant:",nrow(setdiff(sig_tcga_BY$Gene_Codon,sig_genie_BY$Gene_Codon)))
```


# BY - overlap 0
```{r}
# Get the Gene_Codon of non-significant codons in Genie set
nonsig_genie_BY = score_data[which(score_data$Driver_BY == 0),c(1,3)]
print(nrow(nonsig_genie_BY))
nonsig_genie_BY

# Get the Gene_Codon of non-significant codons in TCGA set
nonsig_tcga_BY = test_score_data[which(test_score_data$Driver_BY == 0),c(1,3)]
print(nrow(nonsig_tcga_BY))
nonsig_tcga_BY

# Get the intersected part (0,0)
intersect_0 = intersect(nonsig_genie_BY$Gene_Codon,nonsig_tcga_BY$Gene_Codon)
paste("Both insignificant:",length(intersect_0))

# Get the unintersected part (0,1 / 1,0)
paste("only Genie non-Significant:",length(setdiff(nonsig_genie_BY$Gene_Codon,nonsig_tcga_BY$Gene_Codon)))
paste("Only TCGA non-Significant:",length(setdiff(nonsig_tcga_BY$Gene_Codon,nonsig_genie_BY$Gene_Codon)))
```

# 217 potential driver mutation
```{r}
drivers_BY = sig_genie_BY[which(sig_genie_BY$Gene_Codon %in% intersect_1),]
drivers_BY = arrange(drivers_BY,desc(drivers_BY$Sample_Freq))
drivers_BY
```

```{r}
write.csv(drivers_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_drivers.csv", row.names = FALSE)
```

# 6249 non-driver-BY
```{r}
non_drivers_BY = nonsig_genie_BY[which(nonsig_genie_BY$Gene_Codon %in% intersect_0),]
non_drivers_BY = arrange(non_drivers_BY,desc(non_drivers_BY$Sample_Freq))
non_drivers_BY
```
```{r}
write.csv(non_drivers_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_non_drivers.csv", row.names = FALSE)
```

# significance and non-significance in Genie BY
```{r}
write.csv(sig_genie_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_drivers_genie.csv", row.names = FALSE)
write.csv(nonsig_genie_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_non_drivers_genie.csv", row.names = FALSE)
```


# significance and non-significance in TCGA BY
```{r}
write.csv(sig_tcga_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_drivers_tcga.csv", row.names = FALSE)
write.csv(nonsig_tcga_BY,"/Users/jingjing/SEM2/Dissertations/Project 1/Results/BY_non_drivers_tcga.csv", row.names = FALSE)
```


